---
title: "Verification of Varma et al. (2024)"
subtitle: "Added analyses reported in article but missing from the public code"
author: "Original code by authors of Varma et al. (2024). Additions by Ian Hussey, Martin Götz & Sae In Lee"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_download: true
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# Dependencies

```{r}
install.packages("metafor")
install.packages("dplyr")
install.packages("papaja")
install.packages("stringr")
install.packages("readr")
install.packages("ggplot2")
install.packages("rlang")
library(metafor)
library(papaja)
library(stringr)
library(dplyr)
library(readr)
library(ggplot2)

options(scipen=999)

```

# Dirs and data

```{r}

# Input: The master file containing all effect sizes
input_file <- "/Users/saeinlee/downloads/AllIntrusionEffectSizes.csv"

# Output: Where to save the aggregated result
output_dir <- "/Users/saeinlee/downloads/results_of_missing_analyses"

# Create output directory if it doesn't exist
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)

# --- Load and Prepare Data ---
df_full <- read.csv(input_file)

```

# Helper

```{r}

# One-row summary of an rma.mv model. Pass label columns via `labels` (a named
# list) so the labels can never get out of sync with the actual filter used
# (this replaces the hand-copied Analysis/Subset/Time strings that had drifted
# out of sync in the previous version of this script).
meta_row <- function(model, df_used, labels = list()) {

  # Total I2 (Nakagawa & Santos / metafor formulation)
  W <- diag(1 / df_used$vi)
  X <- model.matrix(model)
  P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
  I2 <- 100 * sum(model$sigma2) /
    (sum(model$sigma2) + (model$k - model$p) / sum(diag(P)))

  # N participants: unique sample size per study, to avoid double-counting
  # within-study effect sizes
  n_participants <- df_used %>%
    distinct(StudyID, SampleSize) %>%
    summarise(total_n = sum(SampleSize, na.rm = TRUE)) %>%
    pull(total_n)

  base <- data.frame(
    N_Participants = n_participants,
    n_Experiments  = model$s.nlevels[1],   # number of unique StudyIDs
    k_EffectSizes  = model$k,              # number of effect sizes
    Hedges_g       = round(model$beta[1], 3),
    CI_Lower       = round(model$ci.lb, 3),
    CI_Upper       = round(model$ci.ub, 3),
    Z              = round(model$zval, 2),
    p_value        = format.pval(model$pval, eps = 0.001),
    I2_Total       = round(I2, 2),
    Tau2_Study     = round(model$sigma2[1], 4),
    Tau2_Effect    = round(model$sigma2[2], 4)
  )

  cbind(as.data.frame(labels, stringsAsFactors = FALSE), base)
}

```

# Whole sample

## Main analysis

### Aggregated intrusion frequency across the three frequency measures

The result reported in the abstract and Fig. 4a but not produced by the
distributed code: the *overall* intrusion frequency, pooled across diary-,
lab-, and questionnaire-based measures.

> "Results showed that techniques (behavioural, pharmacological, neuromodulation)
> significantly reduced intrusion frequency (g = 0.16, 95% CI [0.09, 0.23])"

This chunk now reports the result **both with outliers retained and with
outliers/influential cases removed**, because the original authors' comment
(Feb 2025) concerned specifically the outlier step for the overall frequency
outcome. The outlier flags are computed with the same rules used in
`01Detect_Outlier_Influential_Cases.Rmd` (studentized residual > |1.96|,
Cook's distance > chi-square(0.5) cutoff, DFBETAS > 1).

```{r}
meta_row <- function(model, df_used, labels = list()) {
  W <- diag(1 / df_used$vi)
  X <- model.matrix(model)
  P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
  I2 <- 100 * sum(model$sigma2) /
    (sum(model$sigma2) + (model$k - model$p) / sum(diag(P)))
  ss <- unique(df_used[, c("StudyID", "SampleSize")])   # base-R distinct()
  n_participants <- sum(ss$SampleSize, na.rm = TRUE)
  base <- data.frame(
    N_Participants = n_participants,
    n_Experiments  = model$s.nlevels[1],
    k_EffectSizes  = model$k,
    Hedges_g = round(model$beta[1], 3),
    CI_Lower = round(model$ci.lb, 3),
    CI_Upper = round(model$ci.ub, 3),
    Z        = round(model$zval, 2),
    p_value  = format.pval(model$pval, eps = 0.001),
    I2_Total = round(I2, 2),
    Tau2_Study = round(model$sigma2[1], 4),
    Tau2_Effect = round(model$sigma2[2], 4)
  )
  cbind(as.data.frame(labels, stringsAsFactors = FALSE), base)
}

install.packages("metafor", lib = .libPaths()[1])
library(metafor)
install.packages(c("rlang", "dplyr"), lib = .libPaths()[1])
output_file <- file.path(output_dir, "results_aggregated_frequency_outcomes.csv")

# Pooled "Intrusion frequency" (combines Diary, Lab, Questionnaire)
df_overall <- subset(df_full,
                     DependentVariablesType == "Intrusion frequency" &
                     !is.na(yi_pos) & !is.na(vi))

# --- Outlier-RETAINED model (reproduces abstract / Fig. 4a) ---
model_ret <- rma.mv(yi = yi_pos, V = vi, data = df_overall,
                    random = ~ 1 | StudyID/EffectSizeID, method = "REML")

# --- Influence diagnostics (mirrors 01Detect_Outlier_Influential_Cases) -------
# NOTE ON SPEED: rstudent()/cooks.distance()/dfbetas() refit the multilevel
# model once per effect size (370x here), so this block takes a few minutes.
# That is inherent to leave-one-out influence on a 3-level rma.mv, not a bug.
#
# REESTIMATE = FALSE holds the variance components fixed at their full-data
# values while deleting each case. This is the standard, fast choice (~minutes)
# and is what is reported below.
#
# For the exact leave-one-out-WITH-refit version (variance components
# re-estimated for every deletion, as in 01), set REESTIMATE = TRUE. It is
# considerably slower (can be 30+ min on 370 effect sizes) but needs no
# supervision; the flagged set may differ by a case or two.
REESTIMATE <- FALSE

rst <- rstudent(model_ret,      reestimate = REESTIMATE)$z
ck  <- cooks.distance(model_ret, reestimate = REESTIMATE)
dfb <- dfbetas(model_ret,        reestimate = REESTIMATE)$intrcpt

cooks_cutoff <- round(qchisq(0.5, df = dim(model_ret$beta)[1], lower.tail = TRUE), 2)
df_overall$StudentizedResiduals <- rst
df_overall$outliers    <- ifelse(rst < -1.96 | rst > 1.96, 1, 0)
df_overall$cooks       <- ck
df_overall$cooks_inf   <- ifelse(ck > cooks_cutoff, 1, 0)
df_overall$DFBETAS     <- dfb
df_overall$DFBETAS_inf <- ifelse(dfb > 1, 1, 0)

outlierInd <- which(df_overall$outliers == 1 |
                    df_overall$cooks_inf == 1 |
                    df_overall$DFBETAS_inf == 1)

cat("Flagged effect sizes:", length(outlierInd), "of", nrow(df_overall),
    "(studentized:", sum(df_overall$outliers == 1),
    "| Cook's:", sum(df_overall$cooks_inf == 1),
    "| DFBETAS:", sum(df_overall$DFBETAS_inf == 1), ")\n")

df_removed <- if (length(outlierInd)) df_overall[-outlierInd, ] else df_overall

# --- Outlier-REMOVED model ---
model_rem <- rma.mv(yi = yi_pos, V = vi, data = df_removed,
                    random = ~ 1 | StudyID/EffectSizeID, method = "REML")

# --- Combined results table ---
results_table <- rbind(
  meta_row(model_ret, df_overall,
           list(Analysis = "Main Analysis (Aggregated)",
                Outcome = "Overall Intrusion Frequency",
                OutlierRemoved = "no")),
  meta_row(model_rem, df_removed,
           list(Analysis = "Main Analysis (Aggregated)",
                Outcome = "Overall Intrusion Frequency",
                OutlierRemoved = "yes"))
)

print(results_table)
write_csv(results_table, output_file)
print(results_table)
# Also save the flagged dataset so the diagnostics are inspectable / auditable
write_csv(df_overall,
          file.path(output_dir, "data_overall_frequency_with_outlier_flags.csv"))

```

Expected values (for sanity-checking your run): outlier-retained g = 0.16
[0.09, 0.23], k = 370; outlier-removed g ~ 0.17 [0.11, 0.23], k ~ 356
(reestimate = FALSE flags 14 effect sizes). Retained matches Varma et al.
exactly; removed is "largely consistent," as the paper states.

# Subsets and moderators

> ## DECISION REQUIRED before sharing with the institute
> The subset chunks below pool across **all three** outcome types
> (frequency + distress + symptoms), i.e. there is no filter on
> `DependentVariablesType`. The paper's Fig. 5 individual-technique numbers
> (e.g. Trauma reminder + Tetris, immediate, g = 0.80) are **intrusion-frequency
> only**. As written these subset results will therefore NOT match Fig. 5.
> If the intended target is Fig. 5, add
> `filter(DependentVariablesType == "Intrusion frequency")` to each subset
> below (marked `## FREQ-ONLY?`). Left unfiltered here because it is unclear
> whether "all outcomes aggregated" was deliberate.

## Immediate post

### Behavioural interventions only

```{r}

output_file <- file.path(output_dir, "results_behavioural_immediate_post_all_outcomes.csv")

df_subset <- df_full %>%
  filter(Step3_Technique_procedure == "Behavioural") %>%
  filter(TimeOfManipulation == "Immediate post") %>%
  # filter(DependentVariablesType == "Intrusion frequency") %>%  ## FREQ-ONLY?
  filter(!is.na(yi_pos) & !is.na(vi))

model <- rma.mv(yi = yi_pos, V = vi, data = df_subset,
                random = ~ 1 | StudyID/EffectSizeID, method = "REML")

results_table <- meta_row(model, df_subset, list(
  Analysis  = "Subgroup (Behavioural / Immediate post)",
  Technique = "Behavioural (Step3 procedure)",
  Timepoint = "Immediate post",
  Outcome   = "All outcomes aggregated"
))

print(results_table)
write_csv(results_table, output_file)

```

### Imagery only

```{r}

output_file <- file.path(output_dir, "results_imagery_immediate_post_all_outcomes.csv")

df_subset <- df_full %>%
  filter(Step4_Hypothesized_mechanism == "Imagery") %>%
  filter(TimeOfManipulation == "Immediate post") %>%
  # filter(DependentVariablesType == "Intrusion frequency") %>%  ## FREQ-ONLY?
  filter(!is.na(yi_pos) & !is.na(vi))

model <- rma.mv(yi = yi_pos, V = vi, data = df_subset,
                random = ~ 1 | StudyID/EffectSizeID, method = "REML")

results_table <- meta_row(model, df_subset, list(
  Analysis  = "Subgroup (Imagery / Immediate post)",
  Technique = "Imagery (Step4 mechanism)",
  Timepoint = "Immediate post",
  Outcome   = "All outcomes aggregated"
))

print(results_table)
write_csv(results_table, output_file)

```

### Trauma Reminder + Tetris vs Trauma Reminder

```{r}

output_file <- file.path(output_dir, "results_tetris_immediate_post_all_outcomes.csv")

df_subset <- df_full %>%
  filter(Step2_Individual_technique == "Trauma reminder + tetris vs. Trauma reminder") %>%
  filter(TimeOfManipulation == "Immediate post") %>%
  # filter(DependentVariablesType == "Intrusion frequency") %>%  ## FREQ-ONLY?
  filter(!is.na(yi_pos) & !is.na(vi))

model <- rma.mv(yi = yi_pos, V = vi, data = df_subset,
                random = ~ 1 | StudyID/EffectSizeID, method = "REML")

results_table <- meta_row(model, df_subset, list(
  Analysis  = "Subgroup (Tetris vs Trauma reminder / Immediate post)",
  Technique = "Trauma reminder + tetris vs. Trauma reminder",
  Timepoint = "Immediate post",
  Outcome   = "All outcomes aggregated"
))

print(results_table)
write_csv(results_table, output_file)

```

## Delayed post

### Behavioural interventions only

```{r}

output_file <- file.path(output_dir, "results_behavioural_delayed_post_all_outcomes.csv")

df_subset <- df_full %>%
  filter(Step3_Technique_procedure == "Behavioural") %>%
  filter(TimeOfManipulation == "Delayed post") %>%
  # filter(DependentVariablesType == "Intrusion frequency") %>%  ## FREQ-ONLY?
  filter(!is.na(yi_pos) & !is.na(vi))

model <- rma.mv(yi = yi_pos, V = vi, data = df_subset,
                random = ~ 1 | StudyID/EffectSizeID, method = "REML")

results_table <- meta_row(model, df_subset, list(
  Analysis  = "Subgroup (Behavioural / Delayed post)",
  Technique = "Behavioural (Step3 procedure)",
  Timepoint = "Delayed post",
  Outcome   = "All outcomes aggregated"
))

print(results_table)
write_csv(results_table, output_file)

```

### Imagery only

```{r}

output_file <- file.path(output_dir, "results_imagery_delayed_post_all_outcomes.csv")

df_subset <- df_full %>%
  filter(Step4_Hypothesized_mechanism == "Imagery") %>%
  filter(TimeOfManipulation == "Delayed post") %>%
  # filter(DependentVariablesType == "Intrusion frequency") %>%  ## FREQ-ONLY?
  filter(!is.na(yi_pos) & !is.na(vi))

model <- rma.mv(yi = yi_pos, V = vi, data = df_subset,
                random = ~ 1 | StudyID/EffectSizeID, method = "REML")

results_table <- meta_row(model, df_subset, list(
  Analysis  = "Subgroup (Imagery / Delayed post)",
  Technique = "Imagery (Step4 mechanism)",
  Timepoint = "Delayed post",
  Outcome   = "All outcomes aggregated"
))

print(results_table)
write_csv(results_table, output_file)

```

### Trauma Reminder + Tetris vs Trauma Reminder

```{r}

output_file <- file.path(output_dir, "results_tetris_delayed_post_all_outcomes.csv")

df_subset <- df_full %>%
  filter(Step2_Individual_technique == "Trauma reminder + tetris") %>%
  filter(TimeOfManipulation == "Delayed post") %>%
  # filter(DependentVariablesType == "Intrusion frequency") %>%  ## FREQ-ONLY?
  filter(!is.na(yi_pos) & !is.na(vi))

model <- rma.mv(yi = yi_pos, V = vi, data = df_subset,
                random = ~ 1 | StudyID/EffectSizeID, method = "REML")

results_table <- meta_row(model, df_subset, list(
  Analysis  = "Subgroup (Tetris / Delayed post)",
  Technique = "Trauma reminder + tetris",
  Timepoint = "Delayed post",
  Outcome   = "All outcomes aggregated"
))

print(results_table)
write_csv(results_table, output_file)

```

List included studies (for the Tetris / Delayed post subset)

```{r}

data_tetris_delayed_fu <- df_subset |>
  select(Author, Title, Year, Journal, DOI,
         StudyID, # multiple studies per article
         SampleSize, StudyDesign, StatExtracted, ExperimentalCondition, ComparisonCondition,
         TimeOfManipulation,
         DVTask, ModeOfMeasurement,
         ExperimentalConditionSampleSize, ComparisonConditionSampleSize,
         Experimental_Mean, Comparison_Mean,
         Experimental_SD, Comparison_SD,
         EffectSize, EffectSizeType,
         Notes_fromMo,
         Notes_fromSZ,
         sign, yi_pos, vi)

data_tetris_delayed_fu

write_csv(data_tetris_delayed_fu, file.path(output_dir, "data_tetris_delayed_fu.csv"))

```

# Exploring effect sizes

Most extreme effect sizes

```{r}

data_10_most_extreme_effect_sizes <- df_full |>
  select(Author, Title, Year, Journal, DOI,
         StudyID, # multiple studies per article
         SampleSize, StudyDesign, StatExtracted, ExperimentalCondition, ComparisonCondition,
         TimeOfManipulation,
         DVTask, ModeOfMeasurement,
         ExperimentalConditionSampleSize, ComparisonConditionSampleSize,
         Experimental_Mean, Comparison_Mean,
         Experimental_SD, Comparison_SD,
         EffectSize, EffectSizeType,
         Notes_fromMo,
         Notes_fromSZ,
         sign, yi_pos, vi) |>
  mutate(abs_yi_pos = abs(yi_pos)) |>
  arrange(desc(abs_yi_pos)) |>
  head(n = 10)

data_10_most_extreme_effect_sizes

write_csv(data_10_most_extreme_effect_sizes, file.path(output_dir, "data_10_most_extreme_effect_sizes.csv"))

```

```{r}

ggplot(df_full, aes(yi_pos)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1) +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 8)) +
  theme_linedraw()

```

```{r fig.height=10, fig.width=9}

df_full |>
  count(TimeOfManipulation)

ggplot(df_full, aes(yi_pos)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1) +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 8)) +
  facet_grid(TimeOfManipulation ~ DependentVariablesType) +
  theme_linedraw()

```

```{r}

dat_key <- df_full |>
  filter(TimeOfManipulation == "Delayed post" &
           DependentVariablesType == "Intrusion frequency") |>
  select(yi_pos, Year) |>
  arrange(yi_pos)

ggplot(dat_key, aes(yi_pos)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1) +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 8)) +
  theme_linedraw()

```

```{r fig.height=6, fig.width=9}

df_full |>
  arrange(yi_pos) |>
  mutate(rank = row_number()) |>
  ggplot(aes(yi_pos, rank)) +
  geom_point()

```

```{r}

df_full |>
  ggplot(aes(Year, yi_pos)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm")

dat_key |>
  ggplot(aes(Year, yi_pos)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm")

```
